---
title       : Presentation for coursera project
subtitle    : Step By Step Description For the calculator I made
author      : nilmadhab
job         : 3rd year undergraduate Student of IIT Kharagpur
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Slide 2

Hi everyone!

Welcome to my final project for coursera Developing Data Products.

This course was really wonderful. I learnt a lot here. How to code in R, how to create presentaion and everything else.

---

## Slide 3

There are two input boxs in left side panel.

You need to give enter two numbers in these input boxes.

In main panel, you can see five output boxes.

There is a date input box for fun. You can change the date and same date will be shown in right panel

---

## Slide 4

suppose you entered two number 6 and 3.

Sum  9 will be shown in first output box
as
```{r, echo=TRUE, results='hold'}
6+3
```

differnce 3 will be shown in 2nd output box
```{r, echo=TRUE, results='hold'}
6-3
```


---

## Slide 5


product 18 will be shown in 3rd output box
```{r, echo=TRUE, results='hold'}
6*3
```

division 2 will be shown in 4th output box.
```{r, echo=TRUE, results='hold'}
6/3
```

Thnak you all. It has been wonderful.

---




